---
title: "FML"
author: "Manaswini"
date: "2024-02-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown


#I took this dataset from github, I preferred this dataset because it has both quantitative and qualitative variables.

```{r}

library(readr)
my_data <- read.csv("C:/Users/Winnie/Downloads/HousePrices.csv")

```


summary() function gives brief about the data

```{r}

summary(my_data)

```

#QUANTITATIVE VARIABLE
here I used summary() function and I have choosen "price" as my quantitative variable.
```{r}

summary(my_data$price)

```

#QUALITATIVE VARIABLE
I have choosen lotsize as Qualitative variable.

```{r}

table(my_data$lotsize)

```

#TRANSFORMATION OF QUANTITATIVE VARIABLE
I have transformed my quantitative variable which is Price.

```{r}

my_data$log_transformed_price <- log(my_data$price)
head(my_data)

```

#HISTOGRAM
```{r}

hist(my_data$price)

```



```{r}

hist(my_data$lotsize)

```

#SCATTERPLOT

```{r}

plot(my_data$price)

```



```{r}

plot(my_data$lotsize)

```


#SCATTERPLOT OF BOTH QUANTITATIVE AND QUALITATIVE VARIABLES

```{r}

plot(my_data$price, my_data$lotsize)

```


